On particular diameter bounds for integral point sets in higher dimensions \footnote{ This work was carried out at Voronezh State University and supported by Russian Science Foundation grant 19-11-00197. }

### 2025-03-05 AvdMomZvol_rails/Article.tex
[rails] Inject generated bibliography

\usepackage[backend=biber,style=gost-numeric,sorting=none]{biblatex}
\addbibresource{../common/notmy.bib}
\addbibresource{../common/my.bib}

\usepackage{../../../biblatex2bibitem/biblatex2bibitem}

%\usepackage{cite}

@@

\makeatletter
\ltx@iffilelater{biblatex-gost.def}{2017/02/01}%
{\toggletrue{bbx:gostbibliography}%
\renewcommand*{\revsdnamepunct}{\addcomma}}{}
\makeatother

\printbibliography
\printbibitembibliography
%\bibliography{literature}

%\begin{thebibliography}{99}
%\end{thebibliography}

>>>>

%\usepackage[backend=biber,style=gost-numeric,sorting=none]{biblatex}
%\addbibresource{../common/notmy.bib}
%\addbibresource{../common/my.bib}

%\usepackage{../../../biblatex2bibitem/biblatex2bibitem}

\usepackage{cite}

@@

% The "long" GOST

%\makeatletter
%\ltx@iffilelater{biblatex-gost.def}{2017/02/01}%
%{\toggletrue{bbx:gostbibliography}%
%\renewcommand*{\revsdnamepunct}{\addcomma}}{}
%\makeatother

%\printbibliography
%\printbibitembibliography

% Generated from .bib files with biblatex-gost and biblatex2bibitem

\begin{thebibliography}{99}

{}
\bibitem{ascher2020erdos}
\emph{Ascher}, \emph{K.}, \emph{Braune}, \emph{L.},
\emph{Turchet}, \emph{A.} The Erdős–Ulam problem, Lang’s conjecture and
uniformity / K. Ascher, L. Braune, A. Turchet // Bulletin of the London Mathematical
Society. — 2020. — Vol. 52, no. 6. — Pp. 1053–1063. — arXiv: \href
{http://arxiv.org/abs/1809.02037} {\nolinkurl {1809.02037}}.
{}
\bibitem{solymosi2010question}
\emph{Solymosi}, \emph{J.}, \emph{De Zeeuw}, \emph{F.} On a question of Erdős
and Ulam / J. Solymosi, F. De Zeeuw // Discrete \& Computational Geometry. —
2010. — Vol. 43, no. 2. — Pp. 393–401. — arXiv: \href {http://arxiv.org/abs/0806.3095}
{\nolinkurl {0806.3095}}.
{}
\bibitem{kurz2007enumeration}
\emph{Kurz}, \emph{S.} Enumeration of Integral Tetrahedra / S. Kurz // Journal of
Integer Sequences. — 2007. — Vol. 10, no. 2. — P. 3.{}
\bibitem{anning1945integral}
\emph{Anning}, \emph{N. H.}, \emph{Erdős}, \emph{P.} Integral distances /
N. H. Anning, P. Erdős // Bulletin of the American Mathematical Society. — 1945. —
Vol. 51, no. 8. — Pp. 598–600. — DOI: \href
{https://doi.org/10.1090/S0002-9904-1945-08407-9} {\nolinkurl
{10.1090/S0002-9904-1945-08407-9}}.
{}
\bibitem{erdos1945integral}
\emph{Erdős}, \emph{P.} Integral distances / P. Erdős // Bulletin of the American
Mathematical Society. — 1945. — Vol. 51, no. 12. — P. 996. — DOI: \href
{https://doi.org/10.1090/S0002-9904-1945-08490-0} {\nolinkurl
{10.1090/S0002-9904-1945-08490-0}}.
{}
\bibitem{kemnitz1988punktmengen}
\emph{Kemnitz}, \emph{A.} Punktmengen mit ganzzahligen Abständen /
A. Kemnitz. — 1988.
{}
\bibitem{kurz2005characteristic}
\emph{Kurz}, \emph{S.} On the characteristic of integral point sets in {$\mathbb
{E}^m$} / S. Kurz // Australasian Journal of Combinatorics. — 2006. — Vol. 36. —
Pp. 241–248. — arXiv: \href {http://arxiv.org/abs/math/0511704} {\nolinkurl
{math/0511704}}.
{}
\bibitem{kurz2008bounds}
\emph{Kurz}, \emph{S.}, \emph{Laue}, \emph{R.} Bounds for the minimum
diameter of integral point sets / S. Kurz, R. Laue // Australasian Journal of
Combinatorics. — 2007. — Vol. 39. — Pp. 233–240. — arXiv: \href
{http://arxiv.org/abs/0804.1296} {\nolinkurl {0804.1296}}.
{}
\bibitem{solymosi2003note}
\emph{Solymosi}, \emph{J.} Note on integral distances / J. Solymosi // Discrete \&
Computational Geometry. — 2003. — Vol. 30, no. 2. — Pp. 337–342. — DOI: \href
{https://doi.org/10.1007/s00454-003-0014-7} {\nolinkurl {10.1007/s00454-003-0014-7}}.
{}
\bibitem{my-pps-linear-bound-2019}
\emph{Avdeev}, \emph{N.} On existence of integral point sets and their diameter
bounds / N. Avdeev // Australasian Journal of Combinatorics. — 2020. — Vol. 77,
no. 1. — Pp. 100–116. — arXiv: \href {http://arxiv.org/abs/1906.11926} {\nolinkurl
{1906.11926}}. — URL: \url
{https://ui.adsabs.harvard.edu/abs/2019arXiv190611926A/abstract}.
{}\bibitem{nozaki2013lower}
\emph{Nozaki}, \emph{H.} Lower bounds for the minimum diameter of integral point
sets / H. Nozaki // Australasian Journal of Combinatorics. — 2013. — Vol. 56. —
Pp. 139–143.
{}
\bibitem{our-vmmsh-2018}
\emph{Авдеев}, \emph{Н. Н.}, \emph{Семёнов}, \emph{Е. М.} Множества точек с
целочисленными расстояниями на плоскости и в евклидовом пространстве /
Н. Н. Авдеев, Е. М. Семёнов // Математический форум (Итоги науки. Юг
России). — 2018. — Pp. 217–236.
{}
\bibitem{antonov2008maximal}
\emph{Antonov}, \emph{A. R.}, \emph{Kurz}, \emph{S.} Maximal integral point
sets over {$\mathbb {Z}^2$} / A. R. Antonov, S. Kurz // International Journal of
Computer Mathematics. — 2008. — Vol. 87, no. 12. — Pp. 2653–2676. — DOI: \href
{https://doi.org/10.1080/00207160902993636} {\nolinkurl
{10.1080/00207160902993636}}. — arXiv: \href {http://arxiv.org/abs/0804.1280}
{\nolinkurl {0804.1280}}.
{}
\bibitem{kurz2008minimum}
\emph{Kurz}, \emph{S.}, \emph{Wassermann}, \emph{A.} On the minimum
diameter of plane integral point sets / S. Kurz, A. Wassermann // Ars Combinatoria. —
2011. — Vol. 101. — Pp. 265–287. — arXiv: \href {http://arxiv.org/abs/0804.1307}
{\nolinkurl {0804.1307}}.
{}
\bibitem{zvolinsky2021facher}
\emph{Zvolinsky}, \emph{R. E.} Facher integral point sets with particular distances of
arbitrary cardinality / R. E. Zvolinsky // Актуальные проблемы прикладной
математики, информатики и механики. — 2021. — Pp. 668–674.
{}
\bibitem{lushina2021vestnikpmm}
\emph{Лушина}, \emph{Е. А.}, \emph{Авдеев}, \emph{Н. Н.} О характеристике
плоских множеств с целочисленными расстояниями с рёбрами 1 и 2 /
Е. А. Лушина, Н. Н. Авдеев // Вестник факультета прикладной математики,
информатики и механики. — 2021. — Vol. 15. — Pp. 117–123.
{}
\bibitem{our-ped-2018}
\emph{Авдеев}, \emph{Н. Н.} On integral point sets in special position /
Н. Н. Авдеев // Некоторые вопросы анализа, алгебры, геометрии и
математического образования: материалы международной молодежной научной
школы «Актуальные направления математического анализа и смежные
вопросы». — 2018. — Vol. 8. — Pp. 5–6.{}
\bibitem{our-pmm-2018}
\emph{Авдеев}, \emph{Н. Н.} Об отыскании целоудалённых множеств
специального вида / Н. Н. Авдеев // Актуальные проблемы прикладной
математики, информатики и механики - сборник трудов Международной научной
конференции. — Научно-исследовательские публикации, 2018. — Pp. 492–498.
{}
\bibitem{lushina2025norailswith2}
\emph{Лушина}, \emph{Е. А.} О длине основания рельсового целоудалённого
множества / Е. А. Лушина // Современные проблемы математики и её
приложений. — Институт математики и механики УрО РАН им. Н.Н. Красовского,
2025. — в печати.
{}
\bibitem{harborth1993upper}
\emph{Harborth}, \emph{H.}, \emph{Kemnitz}, \emph{A.},
\emph{Möller}, \emph{M.} An upper bound for the minimum diameter of integral
point sets / H. Harborth, A. Kemnitz, M. Möller // Discrete \& Computational
Geometry. — 1993. — Vol. 9, no. 4. — Pp. 427–432. — DOI: \href
{https://doi.org/10.1007/bf02189331} {\nolinkurl {10.1007/bf02189331}}.
{}
\bibitem{piepmeyer1996maximum}
\emph{Piepmeyer}, \emph{L.} The maximum number of odd integral distances
between points in the plane / L. Piepmeyer // Discrete \& Computational Geometry. —
1996. — Vol. 16, no. 1. — Pp. 113–115. — DOI: \href
{https://doi.org/10.1007/bf02711135} {\nolinkurl {10.1007/bf02711135}}.
{}
\bibitem{bat2018number}
\emph{Bat-Ochir}, \emph{G.} On the number of points with pairwise integral
distances on a circle / G. Bat-Ochir // Discrete Applied Mathematics. — 2018. —
Vol. 254. — Pp. 17–32. — DOI: \href {https://doi.org/10.1016/j.dam.2018.07.004}
{\nolinkurl {10.1016/j.dam.2018.07.004}}.
{}
\bibitem{anning1915discussions}
\emph{Anning}, \emph{N.} Discussions: Relating to a Geometric Representation of
Integral Solutions of Certain Quadratic Equations / N. Anning // The American
Mathematical Monthly. — 1915. — Vol. 22, no. 9. — Pp. 321–321.
{}
\bibitem{undrakh2022refinement}
\emph{Undrakh}, \emph{B.}, \emph{Bat-Ochir}, \emph{G.} Refinement of the upper
bound of the radius of a circular integral points set / B. Undrakh, G. Bat-Ochir // Gulf
Journal of Mathematics. — 2022. — Vol. 12, no. 1. — Pp. 28–40.
{}\bibitem{kreisel2008heptagon}
\emph{Kreisel}, \emph{T.}, \emph{Kurz}, \emph{S.} There are integral heptagons,
no three points on a line, no four on a circle / T. Kreisel, S. Kurz // Discrete \&
Computational Geometry. — 2008. — Vol. 39, no. 4. — Pp. 786–790. — DOI: \href
{https://doi.org/10.1007/s00454-007-9038-6} {\nolinkurl {10.1007/s00454-007-9038-6}}.
{}
\bibitem{kurz2013constructing}
Constructing $7$-clusters / S. Kurz [et al.] // Serdica Journal of Computing. — 2014. —
Vol. 8, no. 1. — Pp. 47–70. — arXiv: \href {http://arxiv.org/abs/1312.2318} {\nolinkurl
{1312.2318}}.
{}
\bibitem{avdeev2021particular}
\emph{Avdeev}, \emph{N.}, \emph{Momot}, \emph{E.},
\emph{Zvolinsky}, \emph{A.} On particular examples of planar integral point sets and
their classification / N. Avdeev, E. Momot, A. Zvolinsky. —. — arXiv: \href
{http://arxiv.org/abs/2102.12462 [math.CO]} {\nolinkurl {2102.12462 [math.CO]}}.
{}
\bibitem{my-semi-general-5-4-bound-2019}
\emph{Avdeev}, \emph{N.} On diameter bounds for planar integral point sets in
semi-general position / N. Avdeev // Chebyshevskii Sbornik. —. — Vol. 22, no. 4. —
Pp. 343–350. — DOI: \href {https://doi.org/10.22405/2226-8383-2021-22-4-343-350}
{\nolinkurl {10.22405/2226-8383-2021-22-4-343-350}}. — arXiv: \href
{http://arxiv.org/abs/1907.09331} {\nolinkurl {1907.09331}}. — URL: \url
{https://ui.adsabs.harvard.edu/abs/2019arXiv190709331A/abstract}.
{}
\bibitem{lushina2024cardinality}
\emph{Лушина}, \emph{Е. А.}, \emph{Бриндюк}, \emph{В. С.} О мощности
плоского целоудаленного множества с ребром 2 / Е. А. Лушина, В. С. Бриндюк //
~74-я Международная студенческая научно-техническая конференция. Материалы.
Астрахань. — 2024. — Pp. 741–743.
{}
\bibitem{guy2013unsolved}
\emph{Guy}, \emph{R.} Unsolved problems in number theory. Vol. 1 / R. Guy. —
Springer Science \& Business Media, 2013. — DOI: \href
{https://doi.org/10.1007/978-1-4757-1738-9} {\nolinkurl {10.1007/978-1-4757-1738-9}}.
{}
\bibitem{momot2022example}
\emph{Momot}, \emph{E. A.}, \emph{Zvolinskiy}, \emph{R. E.},
\emph{Zvolinskiy}, \emph{A. E.} An example of rails integral point set with
cardinality 106 / E. A. Momot, R. E. Zvolinskiy, A. E. Zvolinskiy // Прикладная
математика и фундаментальная информатика. — 2022. — Pp. 114–115.

\end{thebibliography}
